Figures

### 2019-05-10 figures/07_model-selection.Rmd

loo_compare(loo(fit3), loo(fit4))

model_form <- bf(tp ~ maxdepth + iwslavratio + 
                   (1 + corn | hu4vzoneid))
# unlink("../data/mcmc/fit3.rds")
fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
                         data = dt)

>>>>

model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean + soybeans)
# unlink("../data/mcmc/fit5.rds")
fit5 <- get_if_not_exists(brm_fit, "../data/mcmc/fit5.rds", formula = model_form, 
                         data = dt)

loo_compare(loo(fit4), loo(fit5))

quantile(ranef(fit4)$hu4vzoneid[,,2], c(0, 0.05, 0.5, 0.95, 1))
plot(fit4)
